Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Spell check
Split results and discussion sections
Add further description of the type of input data

\section*{Results and Discussion} %{{{1

@@

The distances between contigs may be estimated from paired read data or from
mapping the contigs to a reference genome. These inter-contig gap regions are
useful to join separate sequences together by an estimated size and the
scaffold file allows for the specification of these unknown regions. The use of
these regions in the scaffold which areas in the scaffold and thier approximate
size are still to be resolved. \pb

The scaffold file specifies how sequence regions are joined together; however
the sequences themselves are not stored in the scaffold file and are instead
maintained as a separate FASTA file. A FASTA file of contigs and scaffolded
contigs is a common output for assemblers. The nucleotide sequences stored in
the corresponding FASTA file are referenced in the scaffold using the first
word in the FASTA header. Maintaining the nucleotide sequences in a separate
file preserves the original sequence and decouples the original sequence data
from the scaffold file describing how it should be used to in the genome
sequence. \pb

@@

The first line of the scaffold file begins with three dashes to indicate the
start of a YAML-formatted document. The first entry (highlighted in green)
begins with a dash character `-' to denote an entry in the YAML list. The first
line of each entry in the scaffold therefore begins with a dash line. The next
line is indented by two spaces as whitespace is required to group similar
attributes together. The ``sequence'' tag indicates that this entry corresponds
to a sequence in the FASTA file and the following line indicates the name of
this FASTA sequence using the ``source'' tag. As described the first
space-delimited word of the FASTA header is used to identify which sequence is
selected from the FASTA file. Together these three lines describe the first
entry in the scaffold as a simple sequence using the FASTA sequence named
`sequence1'. On the right hand side of Figure 1 this produces the first region
in the scaffold, also shown in green. \pb

@@

\subsection*{Discussion of Scaffolder Approach} %{{{2

>>>>

\section*{Results} %{{{1

@@

The distances between contigs may be estimated from paired read data or from
mapping the contigs to a reference genome. These inter-contig gap regions are
useful to join separate sequences together by an estimated size and the
scaffold file allows for the specification of these unknown regions. The use of
these regions in the scaffold which areas in the scaffold and their approximate
size are still to be resolved. \pb

The scaffold file specifies how sequence regions are joined together; however
the sequences themselves are not stored in the scaffold file and are instead
maintained as a separate FASTA file. Series of nucleotide sequences in
a FASTA-formatted file is standard output for a genome assembler. These may be
contigs, sets of contigs scaffolded into larger sequences, or both. These
nucleotide sequences stored in the corresponding FASTA file are referenced in
the scaffold using the first word form the FASTA header of the corresponding
nucleotide sequence. Maintaining the nucleotide sequences in a separate file
preserves the original sequence and decouples the original sequence data from
the scaffold file describing how it should be used to in the genome sequence.
\pb

@@

The first line of the scaffold file begins with three dashes to indicate the
start of a YAML-formatted document. The first entry (highlighted in green)
begins with a dash character `-' to denote an entry in the YAML list. The first
line of each entry in the scaffold therefore begins with a dash line. The next
line is indented by two spaces as whitespace is required to group similar
attributes together. The ``sequence'' tag indicates that this entry corresponds
to a sequence in the FASTA file and the following line indicates the name of
this FASTA sequence using the ``source'' tag. As described the first word of
the FASTA header is used to identify which sequence is selected from the file.
Together these three lines describe the first entry in the scaffold as a simple
sequence using the FASTA sequence named `sequence1'. On the right hand side of
Figure 1 this produces the first region in the scaffold, also shown in green.
\pb

@@

\section*{Discussion} %{{{1
